\begin{problem}
    Which of the following are integral domains?
    If they are, describe their respective fields of fractions.
    
    \begin{enumerate}
        \item $\mathbb{Q}[T]$
        \begin{sol}
            It is a domain because $\mathbb{Q}$ is a domain.
            As the field of fractions we get $\mathbb{Q}(T) \coloneqq
            \{\frac{p}{q} \mid p, q \in Q[T]\}$, that is, the set of
            rational functions on one variable.
        \end{sol}
        \item $\mathbb{Z}[T]$
        \begin{sol}
            By the same reasoning, it is an integral domain.
            Note that the homomorphism by the inclusion $\mathbb{Z} \rightarrow \mathbb{Q}$
            from its field of fractions (we shal call it $\mathbb{Z}(T)$)
            into $\mathbb{Q}(T)$ is injective as it is a field homomorphism.
            Furthermore, it is surjective: by taking common denominators, we can express
            any element of $\mathbb{Q}(T)$ as $\frac{p'/a}{q'/b} = \frac{p'b}{q'a}$,
            where $p', q' \in \mathbb{Z}[T]$, $a, b \in \mathbb{Z}$.
            Therefore, the field of fractions of $\mathbb{Z}[T]$ is also $\mathbb{Q}(T)$.
        \end{sol}
        \item $\mathbb{Z}/(T^n)$
        \begin{sol}
            This is not a domain for $n > 1$, as $T^{n-1}T = T^n = 0$,
            but none of the factors is $0$.
            For $n = 1$, it is isomorphic to $\mathbb{Z}$, which is a domain
            with field of fractions $\mathbb{Q}$.
        \end{sol}
        \item  $\mathbb{Z}[T]/(p^n, T), p \in \mathbb{Z}$ prime.
        \begin{sol}
            This is not a domain for $n > 1$, as $p^{n-1}p = p^n = 0$,
            but none of the factors is $0$.
            For $n = 1$, it is isomorphic to $\mathbb{Z}/(p)$, which is a domain
            and in fact a field, so its field of fractions is itself.
        \end{sol}
        \item $\mathbb{Z}[T]/(p, T^n), p \in \mathbb{Z}$ prime.
        \begin{sol}
            This is not a domain for $n > 1$, as $T^{n-1}T = p^n = 0$,
            but none of the factors is $0$.
            For $n = 1$, it is exactly the same as the previous case.
        \end{sol}
        \item $\mathbb{Z}/n\mathbb{Z}[T]$
        \begin{sol}
            This is isomorphic to $\mathbb{Z}[T]/(n)$
            and therefore it is a domain if and only if $(n)$ is prime.
            By the previous exercise, the ideal $(n)\subset\mathbb{Z}[T]$
            is prime if and only if $n$ is prime.
            In that case, its field of fractions is $\mathbb{Z}/n\mathbb{Z}(T)
            = \{\frac{p}{q} \mid p, q \in \mathbb{Z}/n\mathbb{Z}[T]\}$.
        \end{sol}
        \item $A \times B$, where $A$ and $B$ are any given rings.
        \begin{sol}
            This is never domain,
            as $(1, 0)(0, 1) = (0, 0) = 0$,
            but none of the factors is $0$ (we are working with nontrivial rings, $1 \neq 0$).
        \end{sol}
    \end{enumerate}
\end{problem}